Bias no more! A practical guide to latent mean centering in multilevel models

### 2022-12-07 ms.Rmd
Fix typo

# Code example from Ethan McCormick
# Matti's code edited to add `depb` as 'main effect'
# Estimate model without nlf() with depb added to the first formula
# This seems to be slightly different as it adds depb as predictor of urge?
# But under typical conditions these should give similar key estimates (?)
model <- bf(
  urge ~ alpha + phi*(urge1 - alpha) + depb + beta*(dep - depb),
  alpha ~ 1 + (1 | person),  # Latent intercept of urge
  depb ~ 1 + (1 | person),  # Latent mean of depression
  phi ~ 1 + (1 | person),  # Slope of latent mean-person centered lagged urge on urge
  beta ~ 1 + (1 | person),  # Slope of latent mean-person centered depression on urge
  nl = TRUE,
  center = FALSE. # This seems key
) +
  gaussian()

>>>>

# Code example from Ethan McCormick
# Matti's code edited to add `depb` as 'main effect'
# Estimate model without nlf() with depb added to the first formula
# This seems to be slightly different as it adds depb as predictor of urge?
# But under typical conditions these should give similar key estimates (?)
model <- bf(
  urge ~ alpha + phi*(urge1 - alpha) + depb + beta*(dep - depb),
  alpha ~ 1 + (1 | person),  # Latent intercept of urge
  depb ~ 1 + (1 | person),  # Latent mean of depression
  phi ~ 1 + (1 | person),  # Slope of latent mean-person centered lagged urge on urge
  beta ~ 1 + (1 | person),  # Slope of latent mean-person centered depression on urge
  nl = TRUE,
  center = FALSE # This seems key
) +
  gaussian()
